The purpose of this report is to examine the general features and inter-dependancies of the MPG dataset. The dataset itself was compiled by the EPA, and it contains various characteristics about car models released between 1999 and 2008.

First, we need to see what types of vehicles we have in our dataset.
```{r}
ggplot(mpg)+
  geom_bar(aes(x = factor(1), fill = class), width = 1)+
  labs(x = " ", y = "Vehicle Classes")+
  coord_polar(theta = "y")+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())
```

It seems that the dataset is very diverse. It seems that SUVs are a bit more numerous than the other classes. 
Now, we'll try to determine which car class achieves the highest miles per gallon (MPG). In order to do that, we first need to see which variables we should use - City MPG (CMPG), or Highway MPG (HMPG)? 
```{r}
ggplot(mpg, aes(x = cty, y = hwy))+
  geom_smooth()
cor(x = mpg$cty, y = mpg$hwy, use = "everything")
```
The graph above shows that high CMPG correspond with high HMPG, and vice versa. Due to the strong correlation between these variables, future graphs will make use of CMPG. 
```{r}
ggplot(data = mpg)+
  geom_point(mapping = aes(x = displ, y = cty, color = class), position = "jitter",)+
  labs(x = "Displacement", y = "City MPG", title = "City MPG by car class")
```
We can clearly see that lower engine size (displacement) is strongly  correlated with a high MPG. We can get a better look at this relationship if we plot each class of car to a different plot.

```{r}
ggplot(mpg)+
  geom_point(aes(x = displ, y = cty), color = "blue")+
  labs(x = "Displacement", y = "City MPG", title = "City MPG by car class")+
  facet_wrap(~class, nrow = 2)
```

Here we see that compact, subcompact and midsize cars have the best overall MPG, while 2-seaters have the worst MPG out of all classes. This makes sense, since most sports cars (which have the largest engines) are 2-seaters.

The same information can be expressed with a boxplot (shown below).
```{r}
ggplot(mpg, aes(x = class, y = cty))+
  geom_boxplot()
```


```{r}
summary(mpg$cty)
summary(mpg$hwy)
filter(mpg, cty == 35, hwy == 44)
```
We can see that the model with the highest CMPG and HMPG is the 1999 Volkswagen Beetle. It would be interesting to see which manufacturer has the modesl with the highest CMPG and HMPG

```{r}
data <- mpg
    ggplot(mpg)+
    geom_boxplot(aes(x = " ", y = cty, group = 1, fill = manufacturer), position = "dodge",       show.legend = FALSE)+
    labs(x = " ", y = "City MPG")+
    facet_wrap(~manufacturer, nrow = 1)+
    coord_cartesian(ylim = c(0, 30))
  ggplot(mpg)+
    geom_boxplot(aes(x = " ", y = hwy, group = 1, fill = manufacturer), position = "dodge", show.legend = FALSE)+
    labs(x = " ", y = "Highway MPG")+
    facet_wrap(~manufacturer, nrow = 1)+
    coord_cartesian(ylim = c(10, 35))  
```
```{r}
ggplot(mpg)+
  geom_boxplot(aes(x = " ", y = hwy, group = 1, fill = manufacturer), position = "dodge", show.legend = FALSE)+
  labs(x = " ", y = "Highway MPG")+
  facet_wrap(~manufacturer, nrow = 1)+
  coord_cartesian(ylim = c(10, 35))
```

